Robot Team III: Scotty Strikes Back

### 2024-04-04 paper/paper.tex
Updates from Overleaf

\begin{figure}[t]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=15.5cm]{Definitions/logo-mdpi}
\end{adjustwidth}
\caption{This is a wide figure.\label{fig2}}
\end{figure}

>>>>

\begin{figure}[t]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=15.5cm]{paper/figures/methods/sample-spectra.pdf}
\end{adjustwidth}
\caption{(a) Sample hyperspectral data cube. Spectra are plotted using their geographic position with the log10-reflectance colored along the z axis and a pseudo-color image on top. (b) Points taken from a sample hyperspectral data cube corresponding to algae, rhodamine dye, water, and dry grass. (c) The associated spectra for the exemplar points scaled so that the peak value of each spectrum is 1. (d) The location of the pond in Montague, Texas where data were collected for this study.\label{fig:sample-spectra}}
\end{figure}
